Verification of the CVM algorithm with a New Recursive Analysis Technique

### 2025-02-20 paper/sec/formalization_neg_dep.tex
some suggestions

The formalization follows the definitions by Joag-Dev and Proschan~\cite{joagdev1983} closely.
However, the authors did not correctly define the constrains for the possible set of test functions $f$ and $g$ in \cref{def:neg_assoc}, which does not make sense formally.
In the formalization, we assume that the functions are bounded and measurable.
On the other hand, we derive that the condition is still true, if $f, g$ are square integrable.
Or alternatively integrable, and non-negative.
This is derived using the monotone-convergence theorem.

Another deviation from the original work is that we do not require that the random variables need to be real-valued.
In the formalization any linearly ordered topological space with the Borel $\sigma$-algebra is allowed as the range space.
In this case the test functions must be monotone with respect ot the respective order on that space.

@@

>>>>

The formalization follows the definitions by Joag-Dev and Proschan~\cite{joagdev1983} closely.
However, the authors did not correctly define the constraints for the possible set of test functions $f$ and $g$ in \cref{def:neg_assoc}, which does not make sense formally.
In the formalization, we assume that the functions are bounded and measurable.
On the other hand, we derive that the condition is still true, if $f, g$ are square integrable.
Or alternatively integrable, and non-negative.
This is derived using the monotone-convergence theorem.

Another deviation from the original work is that we do not require that the random variables need to be real-valued.
In the formalization any linearly ordered topological space with the Borel $\sigma$-algebra is allowed as the range space.
In this case the test functions must be monotone with respect to the respective order on that space.

@@

\todo{I think we can afford to go into some high-level details of the formalization. Here's what I (YK) suggest}

\begin{itemize}
\item It would be good to show the definition of NA and compare it to Definition 2
\item It would be good to show formalized versions of Prop 3, Lemma 4, and the NA of permutation distributions
\end{itemize}
